MLISA: Machine Learning-based \\ Intelligent Service Agents (to change)

### 2014-07-19 papers/webservice-coalition-learning/webservice_coalition_learning.tex
changes

  \item \emph{Throughput} is the rate at which a service can process requests. QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity. Throughput is a real number in the range $[0, 1]$.

	\item \emph{Availability} is the percentage of time that a service is operating.
	The probability that the service operation is accessible. Availability is also a real number in the range $[0, 1]$.

	\item \emph{Execution Time} is the time a service takes to respond to various types of requests. 
	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
	Execution time is measured in seconds. Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. This internal feature is a positive integer.

@@

>>>>

  \item \emph{Throughput $(Th_{C})$} is the rate at which a service can process requests. QoS measures can include the maximum throughput or a function that describes how throughput varies with load intensity. Throughput is a positive real number. For communities the expected throughput value of collaborating web services can be estimated as:

	\begin{equation}
		 Th_{C} = \left\{ 
			\begin{array}{l l}
				Th_{w} & \quad \text{if $|C| = 1$}\\
				\sum_{w \in C}{(Th_{w})} & \quad \text{if $|C| > 1$}
			\end{array} \right.
	\end{equation}

	\item \emph{Availability $(A_{C})$} is the percentage of time that a service is operating.
	The probability that the service operation is accessible. Availability is also a real number in the range $[0, 1]$. For communities the expected availability of collaborating web services considering they follow a parallel system can be estimated as:

	\begin{equation}
		A_{C} = \left\{ 
			\begin{array}{l l}
				A_{w} & \quad \text{if $|C| = 1$}\\
				1-\prod_{w \in C}{(1-A_{w})} & \quad \text{if $|C| > 1$}
			\end{array} \right.
	\end{equation}

	\item \emph{Execution Time $(Et_{C})$} is the time a service takes to respond to various types of requests. 
	%is the expected delay between the time instant when a request is sent and the time when the result is obtained. 
	Execution time is measured in milliseconds. Execution time can be affected by load intensity, which can be measured in terms of arrival rates (such as requests per second) or number of concurrent requests. This internal feature is a positive integer. For communities the expected execution time of collaborating web services can be estimated as:

	\begin{equation}
		Et_{C} = \left\{ 
			\begin{array}{l l}
				Et_{w} & \quad \text{if $|C| = 1$}\\
				max_{w \in C}{(Et_{w})} & \quad \text{if $|C| > 1$}
			\end{array} \right.
	\end{equation}

@@

A community of web services are abstracted as a standard web service providing services sharing same internal and external features mentioned for web services. Inside, they adopt different protocols to manage the community, however other web services or end users can communicate with communities of web services, using standard protocols and inner details will be encapsulated for their clients.

\subsection{Task Distribution}

Communities of web services usually employ an implementation of Contract-Net protocol for task distribution, in which services opt for incoming tasks, and they will get the tasks if they ask for them. However in our model our community would try to distribute tasks based on their capabilities and QoS parameters the web services have announced. We have used a slightly modified \emph{weighted fair queuing} method to distribute tasks among the members of the community. The goal is to allocate incoming tasks to web services with a rate matching the throughput value of $Th_{ws}$. In the \emph{weighted fair queuing} method, the input flow is multiplexed along different paths, however in our case if the rate of incoming tasks are less than communities total throughput $(Th_{C})$ which is the summation of throughput values of the web services in the community, some of the input tasks will be queued and served with delay. 
%Thus, the amount of tasks performed by the community is $\sum_{ws}{Th_{ws}}$ when $\sum_{ws}{Th_{ws}} \leq R_{C}$. 
However, when incoming task rate is less than the throughput of the community, the \emph{weighted fair queuing} algorithm assigns a weighted task rate of $|input Task Rate| \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each web service ($ws$) within the community.

While distributing tasks, the community members can verify the performance, throughput and quality of service of tasks being performed by web services. The community can recognize if those web services are capable of doing the amount of tasks they advertised. If for any reason there is a decline in the quality metric or throughput, the community can consider the new values as benchmark for future performance calculations, and penalize the suspicious web services. In this way, players will have incentive to truthfully reveal their real capabilities in order to profit best from the community and to avoid being penalized. In addition, the system should be dynamic enough to detect and react to web services quality metrics variation as over time web service metrics may degrade or improve, a change that the community should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

\subsection{Community Revenue (Utility)}

The communities and web services earn revenue by performing tasks. The total gain is function of quality of rate of tasks being performed. 
We have adopted a linear equal weight average over all QoS parameters listed in Table \ref{qosws} excluding the $Throughput$ and $Cost$ parameters. A community has the option to weigh specific QoS parameters depending on the expectations of
their clients.

\begin{equation}\label{out_c}
PO(C) = \sum_{ws \in C}{(T_{ws} \times QoS_{ws})}
\end{equation}

The revenue function of the web service community is a linear
function of $Out(C)$ with a positive constant multiplier. The
worth of a community is set to the output the community can
generate, i.e., $v(C) = Out(C)$.
